---
date: "Date: `r Sys.Date()`"
output:
    html_document:
        toc: true
        toc_depth: 3
        toc_float: true
        theme: cerulean
geometry: margin = 2cm
---

# Results of CAGEr analysis

### Tag region annotation
Annotation of raw tags per samples.
Note: tags are not filtered or normalized yet.
It is expected to see more intergenic reads here than after filtering and clustering which removes much of the noise.
```{r eval=TRUE, include=TRUE, echo=FALSE}
options(warn=-1)
tagannot_plot <- readRDS("tag_region_annotation_plot.rds")
tagannot_plot
```

### Correlation of samples at raw tag count level
Correlation of samples by the raw tag counts.
Note: these are not filtered or normalized yet. The plot is for diagnostic purposes, such as highlighting batch effects.
```{r eval=TRUE, include=TRUE, echo=FALSE}
corr_m <- readRDS("CTSS_correlations_matrix.rds")
hm_plot <- readRDS("CTSS_correlations_plot.rds")
eval(hm_plot$call)
```

### Normalization
Number of CAGE tags versus number of TSS supported by at least as many tags should follow the power-law distribution.
The power-law distribution is fitted in the range between the two dotted lines.
The positions of the dotted lines are modifiable by user with norm_range_min and norm_range_max parameters.
These defaults to 5 and 10000, respectively.
The total number of tags (T_norm) defaults to 1000000 which corresponds to TPM, but in cases of very deep sequencing this should be adjusted.
```{r eval=TRUE, include=TRUE, echo=FALSE}
revc_plot <- readRDS("reverse_cumulative_plot.rds")
revc_plot
```

### Correlations of normalized tags
```{r eval=TRUE, include=TRUE, echo=FALSE}
corr_m <- readRDS("norm_CTSS_correlations_matrix.rds")
hm_plot <- readRDS("norm_CTSS_correlations_plot.rds")
eval(hm_plot$call)
```

### PCA plot of normalized tag counts
```{r eval=TRUE, include=TRUE, echo=FALSE}
pca_plot <- readRDS("CTSS_pca_plot.rds")
pca_plot
```

### Tag cluster interquartile width
Interquartile width distribution in each sample.
A sequencing library of sufficient depth shows two types of tag clusters: narrow and wide.
In low depth cases, the wider type might be lacking which flags low quality data.
```{r eval=TRUE, include=TRUE, echo=FALSE}
iqw_plot <- readRDS("interquartile_width_tagclusters_plot.rds")
iqw_plot
```

### Number of tag clusters per sample
```{r eval=TRUE, include=TRUE, echo=FALSE}
tag_clusters_count_plot <- readRDS("tag_clusters_counts_plot.rds")
tag_clusters_count_plot
```

### Tagcluster annotation
ChipSeeker annotation of genomic regions of tag clusters.
Note: the region labels are extracted from a TxDb generated from GTF file provided by the user.
You may find this file in results/txdb folder.
```{r eval=TRUE, include=TRUE, echo=FALSE}
chta_plot <- readRDS("chipseeker_tagCluster_annotation_plot.rds")
chta_plot
```

### Dinucleotide frequencies in tagclusters weighted by expression (tpm)
Expression-level-aware dinucleotide frequencies at dominant TSSs of tag clusters (sorted by frequencies at the first sample in alphabetical order).
Note: Before clustering, low expressed CTSS are filtered by the user defined thresholds: sample_num_thr and ctss_thr.
By default, these values are 1 sample and 1 TPM meaning that these are low-fidelity TSSs supported by less than 1 normalized tag counts in any of the samples.
```{r eval=TRUE, include=TRUE, echo=FALSE}
dinucl_plot <- readRDS("dinucleotide_frequencies_plot.rds")
dinucl_plot + ggplot2::theme(
    text=ggplot2::element_text(size=5),
    axis.text.x = ggplot2::element_text(angle = 90, size=5),
    axis.text.y = ggplot2::element_text(size=5))
```

### Consensus cluster TPM counts
Consensus clusters are clusters aggregated from tag clusters of different samples which are in close vicinity and pass a tpm threshold.
The maximum distance between the 0.1-0.9 interquartile ranges of tag clusters and TPM thresholds can be set by the user with the consensus_ctss_dist and consensus_ctss_thr parameters (defaults are 100 and 2, respecitvely).
This plot shows the number of non zero consensus clusters per samples, as well as the total number of consensus clusters (union).
```{r eval=TRUE, include=TRUE, echo=FALSE}
cc_plot <- readRDS("consensus_counts_plot.rds")
cc_plot
```

### Consensus cluster PCA
PCA calculated on the TPM values of samples within consensus clusters.
```{r eval=TRUE, include=TRUE, echo=FALSE}
ccp_plot <- readRDS("consensus_clusters_pca_plot.rds")
ccp_plot
```

### Number of active enhancers per sample
```{r eval=TRUE, include=TRUE, echo=FALSE}
enh_count_plot <- readRDS("enhancer_count_per_sample_plot.rds")
enh_count_plot
```

### Annotation of enhancers
```{r eval=TRUE, include=TRUE, echo=FALSE}
enh_annot_plot <- readRDS("chipseeker_enhancer_annotation_plot.rds")
enh_annot_plot
```

### Enhancer PCA
```{r eval=TRUE, include=TRUE, echo=FALSE}
enh_p_plot <- readRDS("enhancer_expression_pca_plot.rds")
enh_p_plot
```
